---
title: 'An undergraduate classroom experiment demonstrates the potential of unconscious bias to influence data collection in animal behaviour'
author: 'Thomas Keaney, Theresa Jones and Raoul Mulder' 
output:
  html_document:
    code_folding: hide
    depth: 1
    number_sections: no
    theme: yeti
    toc: yes
    toc_float: yes
    code_download: true
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE)
```

# Teaching materials

$~$

The `pigeon_video.mp4` file and priming emails sent to students are available in the `Teaching_resources` folder found on the [github repository](https://github.com/tomkeaney/Biased_pigeons) associated with this manuscript.

**‘Hungry forager’ primer**: "The video was recorded just after winter, which is typically the most difficult season of the year for pigeons in terms of feeding and survival. About 30% of pigeons do not survive winter; many that do survive experience a significant loss of body mass and must make the most of every feeding opportunity that arises in order to regain condition."

**‘Satiated forager’ primer**: "The video was recorded late in the afternoon near Jewell railway station, a favourite spot for commuters to feed the pigeons. Moreland Council estimates that locals dump 5-10kg of bread and seed here, creating a superabundant daily food source. By the end of the day, many of the birds are completely satiated and have little or no motivation to feed."

$~$

# Load packages and the data

```{r}
library(tidyverse) # tidy style coding
library(brms) # Bayesian models
library(tidybayes) # Bayesian aesthetics
library(MetBrewer) # colours
library(kableExtra) # tables
library(patchwork) # putting plots together
library(DT) # for search- and saveable tables
library(pander) # for simpler tables
library(png) # to load images
library(grid) # to plot images
```

We collated 89 responses across three years, from 82 students. Four students from the 2021 cohort provided multiple responses; we chose to only include their initial response as we cannot be sure that later responses were made while the students were still unaware of the experiment. One additional response did not provide the indicated expectation of the student, so it was removed from the dataset. The cleaned dataset therefore contains 81 responses from 81 students.

De-identified data can be downloaded directly from the table below (click the CSV button), or from the data folder in the [github repository](https://github.com/tomkeaney/Biased_pigeons) associated with this report.

```{r}

data <- 
  read_csv("data/pigeon_bias_data.csv") %>% 
  mutate(Student_ID = as.factor(Student_ID),
         Year = as.factor(Year),
         Foraging_prop = (Foraging_percentage / 100)) %>%
  filter(First_response == "YES",
         Foraging_percentage != "NA",
         Primer_understood != "NA") %>% 
  select(Student_ID, Year, First_response, everything())

data_peck <- 
  data %>%
  filter(Peck_rate_2 != "NA") %>% 
  pivot_longer(cols = Peck_rate_1:Peck_rate_2, names_to = "Trial",
               values_to = "Peck_rate")
  
# Create a function to build HTML searchable tables

my_data_table <- function(df){
  datatable(
    df, rownames=FALSE,
    autoHideNavigation = TRUE,
    extensions = c("Scroller",  "Buttons"),
    options = list(
      dom = 'Bfrtip',
      deferRender=TRUE,
      scrollX=TRUE, scrollY=400,
      scrollCollapse=TRUE,
      buttons =
        list('pageLength', 'colvis', 'csv', list(
          extend = 'pdf',
          pageSize = 'A4',
          orientation = 'landscape',
          filename = 'full_dataset')),
      pageLength = 81
    )
  )
}

my_data_table(data)
```

**Column explanations**

**Student_ID**: unique, anonymised identifier for each student

**Year**: year that the experiment was conducted.

**Gender**: upon enrollment at The University of Melbourne, students are asked to indicate their title. We identified women as students that answered "Miss" or "Ms" and Men as those who that answered "Mr". Those with entirely missing entries were coded as "NA".

**First_response**: indicates whether this was the initial response provided by the student.

**Bias_treatment**: the primer the observer received, where 'satiated' indicates that the students were provided information prior to a trial that suggested pigeons were fell fed, whereas 'hungry' indicated that the pigeons were in poor condition and hungry.

**Expectation**: we asked the students to indicate whether they thought the pigeons would be hungry or satiated. We included this question to test whether students were appropriately primed by their bias treatment.

**Primer_understood**: did the observer's expectation match the primer they received?

**Foraging_percentage**: the percentage of pigeons that students estimated to be foraging over a 60 second period, while observing a large flock.

**Peck_rate_1**: the number of times a single chosen pigeon pecked the ground over a 60 second period.

**Peck_rate_2**: the number of times a second chosen pigeon pecked the ground over a 60 second period.

**Foraging_prop**: proportion of pigeons estimated to be foraging. 

$~$

# Question 1: is estimation of foraging percentage affected by bias manipulations?

$~$

## Exploring allocation versus expectation 1 {.tabset .tabset-pills}

$~$

We find that **24 of the 82 students** indicated a feeding motivation expectation opposite to that implied by the primer they were allocated. 

This suggests that `Expectation` may be a better predictor of foraging estimation than allocated `Bias_treatment`.

We explicitly assess the effect of treatment and expectation by fitting two models:

1. a model with allocated primer (`Bias_treatment`) as the predictor variable 

2. a model with indicated hunger expectation (`Expectation`) as the predictor variable

$~$

### Model 1: allocated primer

```{r}

# First let's model the effect of bias treatment on foraging estimation 

foraging_model_treatment <- brm(Foraging_prop ~ 0 + Bias_treatment + Year,
                                data = data, family = Beta,
                                prior = c(prior(normal(0, 1.5), class = b),
                                          prior(exponential(1), class = phi)),
                                iter = 6000, warmup = 2000, chains = 4, cores = 4,
                                control = list(adapt_delta = 0.8, max_treedepth = 10),
                                seed = 1, file = "fits/foraging_model_treatment")

foraging_model_treatment

```

**Table S1**. Posterior estimates of the percentage of pigeons foraging, split by the primer that students were allocated.

```{r}
new_data <- expand_grid(Bias_treatment = c("Hungry", "Satiated"),
                        Year = 2023)

new_data %>% 
  left_join(data %>% group_by(Bias_treatment) %>% summarise(`n students` = n())) %>% 
  cbind(fitted(foraging_model_treatment, newdata = new_data, summary = T) %>% 
          as_tibble() %>% 
          mutate(across(1:4, ~ .x *100),
                 across(1:4, round, 2))) %>% 
  rename("Estimated % foraging" = Estimate,
         "Bias treatment" = Bias_treatment) %>% 
  select(-Year) %>% 
  pander(split.cell = 20, split.table = Inf)

```

### Model 2: indicated expectation

```{r}

# fit the same model, except using participant expectation rather than allocated bias treatment

foraging_model_expectation <- brm(Foraging_prop ~ 0 + Expectation + Year,
                                     data = data, family = Beta,
                                     prior = c(prior(normal(0, 1.5), class = b),
                                               prior(exponential(1), class = phi)),
                                     iter = 6000, warmup = 2000, chains = 4, cores = 4,
                                     control = list(adapt_delta = 0.8, max_treedepth = 10),
                                     seed = 1, file = "fits/foraging_model_expectation")


foraging_model_expectation

```

**Table S2**. Posterior estimates of the percentage of pigeons foraging, split by the actual expectation of the students.

```{r}

new_data_2 <- expand_grid(Expectation = c("Hungry", "Satiated"),
                          Year = 2023)

new_data_2 %>% 
  left_join(data %>% group_by(Expectation) %>% summarise(`n students` = n())) %>% 
  cbind(fitted(foraging_model_expectation, newdata = new_data_2, summary = T) %>% 
          as_tibble() %>% 
          mutate(across(1:4, ~ .x *100),
                 across(1:4, round, 2))) %>%  
  rename("Estimated % foraging" = Estimate,
         "Indicated expectation" = Expectation) %>%
  select(-Year) %>% 
  pander(split.cell = 20, split.table = Inf)

```

$~$

## Build Figure 1a-d

$~$

**Get posterior means and difference contrasts**

```{r}

# treatment model

draws_treatment <-
  as_draws_df(foraging_model_treatment) %>% 
  mutate(Hungry = inv_logit_scaled(b_Bias_treatmentHungry + b_Year2023) *100,
         Satiated = inv_logit_scaled(b_Bias_treatmentSatiated + b_Year2023)*100,
         diff_contrast = (Hungry - Satiated)) %>% 
  select(Hungry, Satiated, diff_contrast) %>% 
  pivot_longer(names_to = "Treatment", values_to = "Posterior_estimate", cols = 1:3) %>% 
  mutate(Predictor = "Allocated primer")

p2 <- 
  draws_treatment %>% 
  filter(Treatment != "diff_contrast") %>% 
  ggplot(aes(x = Treatment, y = Posterior_estimate)) + 
  stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
               point_interval = "median_qi", point_fill = "white",
               shape = 21, point_size = 4, stroke = 1.5) +
  scale_fill_manual(values = met.brewer("Hiroshige", 2)) +
  coord_flip() +#ylim = c(25, 55)) +
  #geom_vline(xintercept = 0, linetype = 2) +
  #scale_y_continuous(breaks = c(, 0, 1)) +
  xlab("Allocated primer") +
  ylab("Estimated % pigeons foraging") +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        text = element_text(size = 14))

p3 <-
  draws_treatment %>% 
  filter(Treatment == "diff_contrast") %>% 
  ggplot(aes(y = Posterior_estimate)) + 
   stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
               point_interval = "median_qi", point_fill = "white",
               shape = 21, point_size = 4, stroke = 1.5, scale =0.5) +
  scale_fill_manual(values = met.brewer("Hiroshige")[4]) +
  coord_flip(ylim = c(-20, 20)) +
  geom_hline(yintercept = 0, linetype = 2, linewidth = 0.75) +
  #scale_y_continuous(breaks = c(, 0, 1)) +
  xlab(NULL) +
  ylab("Hungry - Satiated difference\ncontrast (% points)") +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        text = element_text(size = 14))

# expectation model

draws_expectation <-
  as_draws_df(foraging_model_expectation) %>% 
  mutate(Hungry = inv_logit_scaled(b_ExpectationHungry + b_Year2023) *100,
         Satiated = inv_logit_scaled(b_ExpectationSatiated + b_Year2023)*100,
         diff_contrast = (Hungry - Satiated)) %>% 
  select(Hungry, Satiated, diff_contrast) %>% 
  pivot_longer(names_to = "Treatment", values_to = "Posterior_estimate", cols = 1:3) %>% 
  mutate(Predictor = "Indicated expectation")

p4 <-
  draws_expectation %>% 
  filter(Treatment != "diff_contrast") %>% 
  ggplot(aes(x = Treatment, y = Posterior_estimate)) + 
   stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
               point_interval = "median_qi", point_fill = "white",
               shape = 21, point_size = 4, stroke = 1.5) +
  scale_fill_manual(values = met.brewer("Hiroshige", 2)) +
  coord_flip() + #ylim = c(25, 55)) +
  #geom_vline(xintercept = 0, linetype = 2) +
  #scale_y_continuous(breaks = c(, 0, 1)) +
  xlab("Indicated expectation") +
  ylab("Estimated % pigeons foraging") +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        text = element_text(size = 14))

p5 <-
  draws_expectation %>% 
  filter(Treatment == "diff_contrast") %>% 
  ggplot(aes(y = Posterior_estimate)) + 
    stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
               point_interval = "median_qi", point_fill = "white",
               shape = 21, point_size = 4, stroke = 1.5, scale =0.5) +
  scale_fill_manual(values = met.brewer("Hiroshige")[4]) +
  coord_flip(ylim = c(-20, 20)) +
  geom_hline(yintercept = 0, linetype = 2, linewidth = 0.75) +
  #scale_y_continuous(breaks = c(, 0, 1)) +
  xlab(NULL) +
  ylab("Hungry - Satiated difference\ncontrast (% points)") +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        text = element_text(size = 14))
```

$~$

# Question 2: is estimation of feeding rate affected by bias manipulations?

$~$

We asked students to count the number of pecks of the ground that a selected pigeon made over a 1 minute period. We use the number of pecks that occur as a measure of feeding rate.

We first estimated a baseline peck rate by observing 35 pigeons. To select the pigeons we observed, we split a still image of the foraging video (taken at time zero) into a 43 x 21 cell grid. From the 122 cells that contained pigeons, 40 were chosen by random number generation (see code chunk below). In the event that multiple pigeons were present in the cell, we selected the most prominent to observe. Five observations were discarded - three due to overlap of the same pigeon between cells that were selected by the random number generator, and two more as the pigeons left the field of view during the video and could no longer be tracked. 


```{r}
# curly brackets run all lines included within them

{set.seed(1) # so that sample produces a reproducible sequence 
  sample(1:122, 40, replace = FALSE)}
```

The selected pigeons for baseline observation are shown in the image below

```{r}
img <- readPNG("pigeon_selection.png")
 grid.raster(img)
```

**Figure S1**. the pigeons selected for baseline estimation of feeding rate.

$~$

## Estimating baseline feeding rate

$~$

**Load in the data**

```{r}

baseline_data <- read_csv("data/baseline_peck_data.csv") %>% 
  select(1:5) %>%  # remove the comments column
  pivot_longer(cols = 4:5, names_to = "Observation", values_to = "Peck_rate") %>% 
  mutate(ID = as.factor(ID),
         Observation = str_remove(Observation, "Peck_count_")) %>% 
  rename(Pigeon_ID = ID) %>% 
  filter(!is.na(Peck_rate))

my_data_table <- function(df){
  datatable(
    df, rownames=FALSE,
    autoHideNavigation = TRUE,
    extensions = c("Scroller",  "Buttons"),
    options = list(
      dom = 'Bfrtip',
      deferRender=TRUE,
      scrollX=TRUE, scrollY=400,
      scrollCollapse=TRUE,
      buttons =
        list('pageLength', 'colvis', 'csv', list(
          extend = 'pdf',
          pageSize = 'A4',
          orientation = 'landscape',
          filename = 'baseline_dataset')),
      pageLength = 78
    )
  )
}


my_data_table(baseline_data)

```

**X** and **Y** represent grid coordinates.

- **Pigeon_ID** identifies a specific pigeon

- **Observation** indicates whether this was the first or second scoring for a single pigeon. We scored each pigeon twice as distant pigeons were difficult to observe and to ensure that the correct pigeon was tracked throughout the minute of observation.

- **Peck_rate** is the number of times the ground was pecked over a minute of observation.

$~$

**Fit a simple model to estimate median peck rate**

```{r}

baseline_peck_model_zi <-
  brm(Peck_rate ~ 1 + (1|Pigeon_ID),
      family = zero_inflated_negbinomial(), data = baseline_data,
      prior = c( prior(normal(0, 1.5), class = Intercept),
                 prior(exponential(1), class = sd),
                 prior(exponential(1), class = shape),
                 prior(exponential(1), class = zi)),
      chains = 4, cores = 4, warmup = 2000, iter = 6000,
      file = "fits/baseline_peck_model")

# wrangle the output

baseline_peck_predictions <-
  baseline_peck_model_zi %>% 
  as_draws_df() %>% 
  mutate(Baseline_estimate = exp(b_Intercept),
         peck_rate_sd = exp(sd_Pigeon_ID__Intercept)) %>% 
  select(Baseline_estimate, peck_rate_sd)

baseline_data %>% 
  distinct(Pigeon_ID) %>% 
  summarise(`n pigeons observed` = length(Pigeon_ID)) %>%
  bind_cols(
fitted(baseline_peck_model_zi, summary = T, re_formula = NA) %>% 
          as_tibble() %>%
          distinct(Estimate, .keep_all = T) %>% 
          mutate(across(1:4, round, 2)) %>% 
  rename(`Baseline median peck rate / per min` = Estimate)) %>%
  pander()

```

$~$

## Experimental data

$~$

### Exploring allocation versus expectation 2.0 {.tabset .tabset-pills}

$~$

Once again, we hypothesised that attention paid to and/or comprehension of the primer statement had a large effect on student perception of pigeon foraging. 

Lets again fit the two models:

1. a model with allocated primer (`Bias_treatment`) as the predictor variable 

2. a model with indicated hunger expectation (`Expectation`) as the predictor variable

$~$

#### Model 1: allocated primer

```{r}

peck_model_treatment <- 
  brm(Peck_rate ~ 0 + Bias_treatment + Year + (1|Student_ID),
      data = data_peck, family = negbinomial,
      prior = c(prior(normal(0, 1.5), class = b),
                prior(exponential(1), class = sd)),
      iter = 6000, warmup = 2000, chains = 4, cores = 4,
      control = list(adapt_delta = 0.95, max_treedepth = 12),
      seed = 1, file = "fits/peck_model_treatment")

peck_model_treatment

```

**Table S3**. The estimated peck rate of foraging pigeons, split by the primer students were allocated. Each student observed two pigeons.

```{r}
new_data %>% 
  bind_cols(fitted(peck_model_treatment, newdata = new_data, summary = T, re_formula = NA) %>% 
              as_tibble() %>% 
              mutate(across(1:4, round, 2))) %>% 
  left_join(data_peck %>% group_by(Bias_treatment) %>% 
              summarise(`n pigeons observed` = n())) %>% 
  rename("Estimated peck rate" = Estimate,
         "Bias treatment" = Bias_treatment) %>% 
  bind_rows(fitted(baseline_peck_model_zi, summary = T, re_formula = NA) %>% 
              as_tibble() %>%
              distinct(Estimate, .keep_all = T) %>% 
              mutate(across(1:4, round, 2)) %>% 
              rename("Estimated peck rate" = Estimate) %>% 
              mutate(`Bias treatment` = "Baseline") %>% 
              bind_cols(baseline_data %>% 
                          distinct(Pigeon_ID) %>% 
                          summarise(`n pigeons observed` = length(Pigeon_ID)))) %>% 
  select(`Bias treatment`, `n pigeons observed`, `Estimated peck rate`, Est.Error, Q2.5, Q97.5) %>% 
  pander(split.cell = 20, split.table = Inf)

```

#### Model 2: Indicated expectation

```{r}

# fit the same model, except using participant expectation rather than allocated bias treatment

peck_model_expectation <- brm(Peck_rate ~ 0 + Expectation + Year + (1|Student_ID),
                                     data = data_peck, family = negbinomial,
                                     prior = c(prior(normal(0, 1.5), class = b),
                                               prior(exponential(1), class = sd)),
                                     iter = 6000, warmup = 2000, chains = 4, cores = 4,
                                     control = list(adapt_delta = 0.95, max_treedepth = 12),
                                     seed = 1, file = "fits/peck_model_expectation")


peck_model_expectation

```

**Table S4**. The estimated peck rate of foraging pigeons, split by the indicated expectation of the students. Each student observed two pigeons. 

```{r}

new_data_2 %>% 
  bind_cols(fitted(peck_model_expectation, newdata = new_data_2, summary = T, re_formula = NA) %>% 
              as_tibble() %>% 
              mutate(across(1:4, round, 2))) %>% 
  left_join(data_peck %>% group_by(Expectation) %>% 
               summarise(`n pigeons observed` = n())) %>% 
  rename("Estimated peck rate" = Estimate,
         "Indicated expectation" = Expectation) %>% 
  bind_rows(fitted(baseline_peck_model_zi, summary = T, re_formula = NA) %>% 
              as_tibble() %>%
              distinct(Estimate, .keep_all = T) %>% 
              mutate(across(1:4, round, 2)) %>% 
              rename("Estimated peck rate" = Estimate) %>% 
              mutate(`Indicated expectation` = "Baseline") %>% 
              bind_cols(baseline_data %>% 
                          distinct(Pigeon_ID) %>% 
                          summarise(`n pigeons observed` = length(Pigeon_ID)))) %>% 
  select(`Indicated expectation`, `n pigeons observed`, `Estimated peck rate`, Est.Error, Q2.5, Q97.5) %>% 
  pander(split.cell = 20, split.table = Inf)

```

$~$

### Build Figure 1e-h

$~$

**Get posterior means and difference contrasts**

```{r}

# treatment model

peck_draws_treatment <-
  as_draws_df(peck_model_treatment) %>% 
  mutate(Hungry = exp(b_Bias_treatmentHungry + b_Year2023),
         Satiated = exp(b_Bias_treatmentSatiated + b_Year2023),
         diff_contrast = (Hungry - Satiated)) %>% 
  select(Hungry, Satiated, diff_contrast) %>%
  bind_cols(baseline_peck_predictions %>% select(Baseline_estimate)) %>% 
  pivot_longer(names_to = "Treatment", values_to = "Posterior_estimate", cols = 1:3) %>% 
  mutate(Predictor = "Allocated primer")


p6 <- 
    peck_draws_treatment %>% 
    filter(Treatment != "diff_contrast") %>% 
    ggplot(aes(x = Treatment, y = Posterior_estimate)) +
    stat_slab(aes(y = Baseline_estimate),
              linetype = 2, linewidth = 0.8, slab_fill = "white",
              colour = "black") +
    stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
                 point_interval = "median_qi", point_fill = "white",
                 shape = 21, point_size = 4, stroke = 1.5) +
    scale_fill_manual(values = met.brewer("Hiroshige", 2)) +
    coord_flip(ylim = c(0, 20)) +
    #geom_vline(xintercept = 0, linetype = 2) +
    #scale_y_continuous(breaks = c(, 0, 1)) +
    xlab("Allocated primer") +
    ylab("Estimated pecks per min") +
    theme_bw() + 
    theme(legend.position = "none",
          panel.grid.minor = element_blank(),
          text = element_text(size = 14))

p7 <-
  peck_draws_treatment %>% 
  filter(Treatment == "diff_contrast") %>% 
  ggplot(aes(y = Posterior_estimate)) + 
   stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
               point_interval = "median_qi", point_fill = "white",
               shape = 21, point_size = 4, stroke = 1.5, scale =0.5) +
  scale_fill_manual(values = met.brewer("Hiroshige")[4]) +
  coord_flip(ylim = c(-5, 12)) +
  geom_hline(yintercept = 0, linetype = 2, linewidth = 0.75) +
  #scale_y_continuous(breaks = c(, 0, 1)) +
  xlab(NULL) +
  ylab("Hungry - Satiated difference\ncontrast (pecks per min)") +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        text = element_text(size = 14))

# expectation model

peck_draws_expectation <-
  as_draws_df(peck_model_expectation) %>% 
  mutate(Hungry = exp(b_ExpectationHungry + b_Year2023),
         Satiated = exp(b_ExpectationSatiated + b_Year2023),
         diff_contrast = (Hungry - Satiated)) %>% 
  select(Hungry, Satiated, diff_contrast) %>% 
  bind_cols(baseline_peck_predictions %>% select(Baseline_estimate)) %>% 
  pivot_longer(names_to = "Treatment", values_to = "Posterior_estimate", cols = 1:3) %>% 
  mutate(Predictor = "Allocated primer")

p8 <-
  peck_draws_expectation %>% 
  filter(Treatment != "diff_contrast") %>% 
  ggplot(aes(x = Treatment, y = Posterior_estimate)) + 
  stat_slab(aes(y = Baseline_estimate),
              linetype = 2, linewidth = 0.8, slab_fill = "white",
              colour = "black") +
    stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
               point_interval = "median_qi", point_fill = "white",
               shape = 21, point_size = 4, stroke = 1.5) +
  scale_fill_manual(values = met.brewer("Hiroshige", 2)) +
  coord_flip(ylim = c(0, 20)) +
  #geom_vline(xintercept = 0, linetype = 2) +
  #scale_y_continuous(breaks = c(, 0, 1)) +
  xlab("Indicated expectation") +
  ylab("Estimated pecks per min") +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        text = element_text(size = 14))

p9 <-
  peck_draws_expectation %>% 
  filter(Treatment == "diff_contrast") %>% 
  ggplot(aes(y = Posterior_estimate)) + 
   stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
               point_interval = "median_qi", point_fill = "white",
               shape = 21, point_size = 4, stroke = 1.5, scale =0.5) +
  scale_fill_manual(values = met.brewer("Hiroshige")[4]) +
  coord_flip(ylim = c(-5, 12)) +
  geom_hline(yintercept = 0, linetype = 2, linewidth = 0.75) +
  #scale_y_continuous(breaks = c(, 0, 1)) +
  xlab(NULL) +
  ylab("Hungry - Satiated difference\ncontrast (pecks per min)") +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        text = element_text(size = 14))
```

$~$

### Find the difference between baseline and observer estimates

**Table S5**. The degree to which each group of students overestimated feeding rate (number of ground pecks per minute)

```{r}
baseline_peck_predictions %>% select(Baseline_estimate) %>%  bind_cols(
  
  as_draws_df(peck_model_treatment) %>% 
    mutate(Hungry = exp(b_Bias_treatmentHungry + b_Year2023),
           Satiated = exp(b_Bias_treatmentSatiated + b_Year2023)) %>% 
    select(Hungry, Satiated)) %>% 
  mutate(`Bias treatment Satiated / Baseline` = Satiated / Baseline_estimate,
         `Bias treatment Hungry / Baseline` = Hungry / Baseline_estimate) %>% 
  select(contains("Bias")) %>% 
  pivot_longer(cols = everything(), values_to = "estimate", names_to = "Stat") %>% 
  group_by(Stat) %>% 
  summarise_draws("median", "sd", ~quantile(.x, probs = c(0.025, 0.975), na.rm = TRUE), .cores = 4) %>% 
  select(-variable) %>% 
  
  bind_rows(
    
    baseline_peck_predictions %>% select(Baseline_estimate) %>%  bind_cols(
      
      as_draws_df(peck_model_expectation) %>% 
        mutate(Hungry = exp(b_ExpectationHungry + b_Year2023),
               Satiated = exp(b_ExpectationSatiated + b_Year2023)) %>% 
        select(Hungry, Satiated)) %>% 
      mutate(`Expectation Satiated / Baseline` = Satiated / Baseline_estimate,
             `Expectation Hungry / Baseline` = Hungry / Baseline_estimate) %>% 
      select(contains("Expectation")) %>% 
      pivot_longer(cols = everything(), values_to = "estimate", names_to = "Stat") %>% 
      group_by(Stat) %>% 
      summarise_draws("median", "sd", ~quantile(.x, probs = c(0.025, 0.975), na.rm = TRUE), .cores = 4) %>% 
      select(-variable)
  ) %>%
  rename(Median = median,
         Q2.5 = `2.5%`,
         Q97.5 = `97.5%`,
         Est.Error = sd) %>%
  ungroup() %>% 
  mutate(across(2:5, round, 2)) %>% 
  pander(split.cell = 20, split.table = Inf)
```

# Figure 1

Option 1

```{r, fig.height=12, width = 10}
(p2 + p3) / (p4 + p5) / (p6 + p7) / (p8 + p9) +
   plot_annotation(tag_levels = 'a')
```

**Figure 1**. Posterior mean estimates and difference contrasts for observer estimated group foraging percentage and individual feeding rates. The coloured area is the posterior distribution and the white point is the mean estimate with associated 67% and 95% credible intervals. The distributions shown with dashed lines are the posterior for baseline peck rate, estimated from a random sample of pigeons appearing in the video.


# Session info

```{r}
sessionInfo() %>% pander
```

