---
title: 'Observational bias in behavioural ecology: a case study and teaching tool'
author: 'Thomas Keaney, Theresa Jones and Raoul Mulder' 
output:
  html_document:
    code_folding: hide
    depth: 1
    number_sections: no
    theme: yeti
    toc: yes
    toc_float: yes
    code_download: true
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE)
```

```{r}
library(tidyverse) # tidy style coding
library(brms) # Bayesian models
library(loo) # for information criteria
library(tidybayes) # Bayesian aesthetics
library(MetBrewer) # colours
library(kableExtra) # tables
library(patchwork) # putting plots together
library(DT) # for search- and saveable tables
library(pander) # for simpler tables
library(png) # to load images
library(grid) # to plot images
library(ggdag) # to draw dags
```

# Load in the data

We analyse data collected across three cohorts of students (2021-2023) enrolled in the third year School of Biosciences subject, _Animal Behaviour_, at The University of Melbourne. We hereafter refer to students as observers.

```{r}

data <- read_csv("data/pigeon_data.csv") %>% 
  mutate(Student_ID = as.factor(Student_ID),
         Year = as.factor(Year),
         Foraging_prop = (Foraging_percentage / 100)) %>%
  filter(Year %in% c("2021", "2022", "2023"),
         Foraging_percentage != "NA",
         Primer_understood != "NA") %>%
  filter(Student_ID != "60" & Student_ID != "68" & Student_ID != "70" & Student_ID != "72") %>% # remove students that completed the task multiple times
  #Student_ID %in% c("60", "68", "70", "72")) %>% 
  select(-c(First_name, Surname, Peck_mean)) %>%  # remove names when ready
  rename(Observer_ID = Student_ID)

data_peck <- 
  data %>%
  filter(Peck_rate_2 != "NA") %>% 
  pivot_longer(cols = Peck_rate_1:Peck_rate_2, names_to = "Trial",
               values_to = "Peck_rate")
  
# Create a function to build HTML searchable tables

my_data_table <- function(df){
  datatable(
    df, rownames=FALSE,
    autoHideNavigation = TRUE,
    extensions = c("Scroller",  "Buttons"),
    options = list(
      dom = 'Bfrtip',
      deferRender=TRUE,
      scrollX=TRUE, scrollY=400,
      scrollCollapse=TRUE,
      buttons =
        list('pageLength', 'colvis', 'csv', list(
          extend = 'pdf',
          pageSize = 'A4',
          orientation = 'landscape',
          filename = 'full_dataset')),
      pageLength = 78
    )
  )
}


my_data_table(data)

```

**Column explanations**

**Observer_ID**: unique, anonymised identifier for each observer.

**Year**: year that the experiment was conducted

**Bias_treatment**: the primer the observer received, where 'satiated' indicates that the observers were provided information prior to a trial that suggested pigeons were fell fed, whereas 'hungry' indicated that the pigeons were in poor condition and hungry.

**Expectation**: we asked the observers to indicate whether they thought the pigeons would be hungry or satiated. We included this question to test whether observers were appropriately primed by their bias treatment.

**Primer_understood**: did the observer's expectation match the primer they received?

**Foraging_percentage**: the percentage of pigeons that observers estimated to be foraging over a 15 second period, while observing a large flock.

**Peck_rate_1**: the number of times a single chosen pigeon pecked the ground over a 15 second period.

**Peck_rate_2**: the number of times a second chosen pigeon pecked the ground over a 15 second period.

**Foraging_prop**: proportion of pigeons estimated to be foraging 

$~$

# Question 1: is estimation of foraging percentage affected by bias manipulations?

$~$

## Exploring allocation versus expectation 1 {.tabset .tabset-pills}

$~$

We find that **22 of the 78 observers** indicated a feeding motivation expectation opposite to that implied by the primer they were allocated. 

This suggests that `Expectation` may be a better predictor of foraging estimation than allocated `Bias_treatment`. The relationship between these and all other variables that we expect to play a role in this system are depicted in Figure 1.

We explicitly assess the effect of treatment and expectation by fitting two models:

1. a model with allocated primer (`Bias_treatment`) as the predictor variable 

2. a model with indicated hunger expectation (`Expectation`) as the predictor variable

$~$

```{r}
gg_simple_dag <- function(d) {
  
  d %>% 
    ggplot(aes(x = x, y = y, xend = xend, yend = yend, colour = Variables)) +
    geom_dag_point() +
    scale_colour_manual(values = c("Included" = met.brewer("Hiroshige")[4], "Not included" = "grey80")) +
    geom_dag_text(color = met.brewer("Hiroshige")[7]) +
    geom_dag_edges() + 
    theme_dag()
}


observer_bias_dag <- dagify(EF ~ PE + SB + TF,
        PE ~ BT,
        SB ~ PE,
       labels = c("TF" = "True\n Foraging", 
                  "EF" = "Estimated\n Foraging",
                  "PE" = "Prior\n Expectation",
                  "BT" = "Bias\n Treatment",
                  "SB" = "Selection\n Bias")) %>% 
  tidy_dagitty()
  
  
 observer_bias_dag <- left_join(observer_bias_dag$data, tibble(name = c("BT", "EF", "PE", "SB", "TF"),
                                   Variables = c("Included", "Included", "Included", "Not included", "Not included"))) %>% 
   
 gg_simple_dag()


observer_bias_dag

```

**Figure 1**. A direct acrylic diagram showing the flow of causation in our biological system. Our bias treatment (BT) was designed to affect the prior expectation (PE) of the observer's. Prior expectations may affect the estimated level of foraging (EF) directly, or more specifically through biased selection of particular foragers (SB). Estimated foraging is also affected by the true level of foraging (TF) carried out by the flock of pigeons in the footage. We hypothesised that _a priori_ expectations of observer's would affect their foraging estimates. The coloured path shows that this can be tested by modelling the effect of bias treatment on estimated foraging, or alternatively by directly modelling the effect of prior expectation on estimated foraging. 

$~$

### Model 1: allocated primer

```{r}

# First let's model the effect of bias treatment on foraging estimation 

foraging_model_treatment <- brm(Foraging_prop ~ 0 + Bias_treatment,
                                     data = data, family = Beta,
                                     prior = c(prior(normal(0, 1.5), class = b),
                                               prior(exponential(1), class = phi)),
                                     iter = 6000, warmup = 2000, chains = 4, cores = 4,
                                     control = list(adapt_delta = 0.8, max_treedepth = 10),
                                     seed = 1, file = "fits/foraging_model_treatment")

foraging_model_treatment <- add_criterion(foraging_model_treatment, criterion = "loo", file = "fits/foraging_model_treatment")

foraging_model_treatment

```

**Table S1**. Posterior estimates of the percentage of pigeon feeding rate, split by the primer observers were allocated.

```{r}
new_data_2 <- tibble(Bias_treatment = c("Hungry", "Satiated"))

new_data_2 %>% 
  cbind(fitted(foraging_model_treatment, newdata = new_data_2, summary = T) %>% 
          as_tibble() %>% 
          mutate(across(1:4, ~ .x *100),
                 across(1:4, round, 2))) %>% 
  rename("Estimated proportion foraging" = Estimate,
         "Bias treatment" = Bias_treatment) %>% 
  pander()
```


### Model 2: indicated expectation

```{r}

# fit the same model, except using participant expectation rather than allocated bias treatment

foraging_model_expectation <- brm(Foraging_prop ~ 0 + Expectation,
                                     data = data, family = Beta,
                                     prior = c(prior(normal(0, 1.5), class = b),
                                               prior(exponential(1), class = phi)),
                                     iter = 6000, warmup = 2000, chains = 4, cores = 4,
                                     control = list(adapt_delta = 0.8, max_treedepth = 10),
                                     seed = 1, file = "fits/foraging_model_expectation")

foraging_model_expectation <- add_criterion(foraging_model_expectation, criterion = "loo", file = "fits/foraging_model_expectation")

foraging_model_expectation
```

**Table S2**. Posterior estimates of the percentage of pigeons foraging, split by the actual expectation of observers.

```{r}

new_data_3 <- tibble(Expectation = c("Hungry", "Satiated"))

new_data_3 %>% 
  cbind(fitted(foraging_model_expectation, newdata = new_data_3, summary = T) %>% 
          as_tibble() %>% 
          mutate(across(1:4, ~ .x *100),
                 across(1:4, round, 2))) %>%  
  rename("Estimated proportion foraging" = Estimate,
         "Indicated expectation" = Expectation) %>% 
  pander()
```

$~$

## Build Figure 2a-d

$~$

**Get posterior means and difference contrasts**

```{r}

# treatment model

draws_treatment <-
  as_draws_df(foraging_model_treatment) %>% 
  mutate(Hungry = inv_logit_scaled(b_Bias_treatmentHungry) *100,
         Satiated = inv_logit_scaled(b_Bias_treatmentSatiated)*100,
         diff_contrast = (Hungry - Satiated)) %>% 
  select(Hungry, Satiated, diff_contrast) %>% 
  pivot_longer(names_to = "Treatment", values_to = "Posterior_estimate", cols = 1:3) %>% 
  mutate(Predictor = "Allocated primer")

p2 <- 
  draws_treatment %>% 
  filter(Treatment != "diff_contrast") %>% 
  ggplot(aes(x = Treatment, y = Posterior_estimate)) + 
  stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
               point_interval = "median_qi", point_fill = "white",
               shape = 21, point_size = 4, stroke = 1.5) +
  scale_fill_manual(values = met.brewer("Hiroshige", 2)) +
  coord_flip(ylim = c(25, 55)) +
  #geom_vline(xintercept = 0, linetype = 2) +
  #scale_y_continuous(breaks = c(, 0, 1)) +
  xlab("Allocated primer") +
  ylab("Estimated % pigeons foraging") +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        text = element_text(size = 14))

p3 <-
  draws_treatment %>% 
  filter(Treatment == "diff_contrast") %>% 
  ggplot(aes(y = Posterior_estimate)) + 
   stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
               point_interval = "median_qi", point_fill = "white",
               shape = 21, point_size = 4, stroke = 1.5, scale =0.5) +
  scale_fill_manual(values = met.brewer("Hiroshige")[4]) +
  coord_flip(ylim = c(-20, 20)) +
  geom_hline(yintercept = 0, linetype = 2, linewidth = 0.75) +
  #scale_y_continuous(breaks = c(, 0, 1)) +
  xlab(NULL) +
  ylab("Hungry - Satiated difference\ncontrast (% points)") +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        text = element_text(size = 14))

# expectation model

draws_expectation <-
  as_draws_df(foraging_model_expectation) %>% 
  mutate(Hungry = inv_logit_scaled(b_ExpectationHungry) *100,
         Satiated = inv_logit_scaled(b_ExpectationSatiated)*100,
         diff_contrast = (Hungry - Satiated)) %>% 
  select(Hungry, Satiated, diff_contrast) %>% 
  pivot_longer(names_to = "Treatment", values_to = "Posterior_estimate", cols = 1:3) %>% 
  mutate(Predictor = "Indicated expectation")

p4 <-
  draws_expectation %>% 
  filter(Treatment != "diff_contrast") %>% 
  ggplot(aes(x = Treatment, y = Posterior_estimate)) + 
   stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
               point_interval = "median_qi", point_fill = "white",
               shape = 21, point_size = 4, stroke = 1.5) +
  scale_fill_manual(values = met.brewer("Hiroshige", 2)) +
  coord_flip(ylim = c(25, 55)) +
  #geom_vline(xintercept = 0, linetype = 2) +
  #scale_y_continuous(breaks = c(, 0, 1)) +
  xlab("Indicated expectation") +
  ylab("Estimated % pigeons foraging") +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        text = element_text(size = 14))

p5 <-
  draws_expectation %>% 
  filter(Treatment == "diff_contrast") %>% 
  ggplot(aes(y = Posterior_estimate)) + 
    stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
               point_interval = "median_qi", point_fill = "white",
               shape = 21, point_size = 4, stroke = 1.5, scale =0.5) +
  scale_fill_manual(values = met.brewer("Hiroshige")[4]) +
  coord_flip(ylim = c(-20, 20)) +
  geom_hline(yintercept = 0, linetype = 2, linewidth = 0.75) +
  #scale_y_continuous(breaks = c(, 0, 1)) +
  xlab(NULL) +
  ylab("Hungry - Satiated difference\ncontrast (% points)") +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        text = element_text(size = 14))
```

$~$

# Question 2: is estimation of feeding rate affected by bias manipulations?

$~$

We asked observers to count the number of pecks of the ground that a selected pigeon made over a 1 minute period. We use the number of pecks that occur as a measure of feeding rate.

We first estimated a baseline peck rate by observing 35 pigeons. To select the pigeons we observed, we split a still image of the foraging video (taken at time zero) into a 43 x 21 cell grid. From the 122 cells that contained pigeons, 40 were chosen by random number generation (see code chunk below). In the event that multiple pigeons were present in the cell, we selected the most prominent to observe. Five observations were discarded - three due to overlap of the same pigeon between cells that were selected by the random number generator, and two more as the pigeons left the field of view during the video and could no longer be tracked. 


```{r}
# curly brackets run all lines included within them

{set.seed(1) # so that sample produces a reproducible sequence 
  sample(1:122, 40, replace = FALSE)}
```

The selected pigeons for baseline observation are shown in the image below

```{r}
img <- readPNG("pigeon_selection.png")
 grid.raster(img)
```


$~$

## Estimating baseline feeding rate

$~$

**Load in the data**

```{r}

baseline_data <- read_csv("data/baseline_peck_data.csv") %>% 
  select(1:5) %>%  # remove the comments column
  pivot_longer(cols = 4:5, names_to = "Observation", values_to = "Peck_rate") %>% 
  mutate(ID = as.factor(ID),
         Observation = str_remove(Observation, "Peck_count_")) %>% 
  rename(Pigeon_ID = ID) %>% 
  filter(!is.na(Peck_rate))

my_data_table <- function(df){
  datatable(
    df, rownames=FALSE,
    autoHideNavigation = TRUE,
    extensions = c("Scroller",  "Buttons"),
    options = list(
      dom = 'Bfrtip',
      deferRender=TRUE,
      scrollX=TRUE, scrollY=400,
      scrollCollapse=TRUE,
      buttons =
        list('pageLength', 'colvis', 'csv', list(
          extend = 'pdf',
          pageSize = 'A4',
          orientation = 'landscape',
          filename = 'baseline_dataset')),
      pageLength = 78
    )
  )
}


my_data_table(baseline_data)

```

- `X` and `Y` represent grid coordinates.

- `Pigeon_ID` identifies a specific pigeon

- `Observation` indicates whether this was the first or second scoring for a single pigeon. We scored each pigeon twice as distant pigeons were difficult to observe and to ensure that the correct pigeon was tracked throughout the minute of observation.

- `Peck_rate` is the number of times the ground was pecked over a minute of observation.

$~$

**Fit a simple model to estimate median peck rate**

```{r}

baseline_peck_model_zi <-
  brm(Peck_rate ~ 1 + (1|Pigeon_ID),
      family = zero_inflated_negbinomial(), data = baseline_data,
      prior = c( prior(normal(0, 1.5), class = Intercept),
                 prior(exponential(1), class = sd),
                 prior(exponential(1), class = shape),
                 prior(exponential(1), class = zi)),
      chains = 4, cores = 4, warmup = 2000, iter = 6000,
      file = "fits/baseline_peck_model")

# wrangle the output

baseline_peck_predictions <-
  baseline_peck_model_zi %>% 
  as_draws_df() %>% 
  mutate(Baseline_estimate = exp(b_Intercept),
         peck_rate_sd = exp(sd_Pigeon_ID__Intercept)) %>% 
  select(Baseline_estimate, peck_rate_sd)


fitted(baseline_peck_model_zi, summary = T, re_formula = NA) %>% 
          as_tibble() %>%
          distinct(Estimate, .keep_all = T) %>% 
          mutate(across(1:4, round, 2)) %>% 
  rename(`Baseline median peck rate / per min` = Estimate) %>% 
  pander()

```

$~$

## Experimental data

$~$

### Exploring allocation versus expectation 2.0 {.tabset .tabset-pills}

$~$

Once again, we expect that attention paid to and/or comprehension of the primer statement has a large effect on observers' perception of pigeon foraging. 

Lets again fit our two models:

1. a model with allocated primer (`Bias_treatment`) as the predictor variable 

2. a model with indicated hunger expectation (`Expectation`) as the predictor variable

$~$

#### Model 1: allocated primer

```{r}

# First let's model the effect of bias treatment on peck rate

peck_model_treatment <- brm(Peck_rate ~ 0 + Bias_treatment + (1|Observer_ID),
                                     data = data_peck, family = negbinomial,
                                     prior = c(prior(normal(0, 1.5), class = b),
                                               prior(exponential(1), class = sd)),
                                     iter = 6000, warmup = 2000, chains = 4, cores = 4,
                                     control = list(adapt_delta = 0.9, max_treedepth = 12),
                                     seed = 1, file = "fits/peck_model_treatment")

peck_model_treatment <- add_criterion(peck_model_treatment, criterion = "loo", file = "fits/peck_model_treatment")
  
peck_model_treatment
```

**Table S3**. The estimated peck rate of foraging pigeons, split by the primer observers were allocated.

```{r}
new_data_2 %>% 
  cbind(fitted(peck_model_treatment, newdata = new_data_2, summary = T, re_formula = NA) %>% 
          as_tibble() %>% 
          mutate(across(1:4, round, 2))) %>% 
  rename("Estimated peck rate" = Estimate,
         "Bias treatment" = Bias_treatment) %>% 
  rbind(fitted(baseline_peck_model_zi, summary = T, re_formula = NA) %>% 
          as_tibble() %>%
          distinct(Estimate, .keep_all = T) %>% 
          mutate(across(1:4, round, 2)) %>% 
  rename("Estimated peck rate" = Estimate) %>% 
  mutate(`Bias treatment` = "Baseline")) %>% 
  pander()

```

#### Model 2: Indicated expectation

```{r}

# fit the same model, except using participant expectation rather than allocated bias treatment

peck_model_expectation <- brm(Peck_rate ~ 0 + Expectation + (1|Observer_ID),
                                     data = data_peck, family = negbinomial,
                                     prior = c(prior(normal(0, 1.5), class = b),
                                               prior(exponential(1), class = sd)),
                                     iter = 6000, warmup = 2000, chains = 4, cores = 4,
                                     control = list(adapt_delta = 0.95, max_treedepth = 12),
                                     seed = 1, file = "fits/peck_model_expectation")

peck_model_expectation <- add_criterion(peck_model_expectation, criterion = "loo", file = "fits/peck_model_expectation")


peck_model_expectation
#loo_compare(peck_model_treatment, peck_model_expectation)
```

**Table S4**. The estimated peck rate of foraging pigeons, split by the indicated expectation of the observers.

```{r}
new_data_2 %>% 
  cbind(fitted(peck_model_expectation, newdata = new_data_3, summary = T, re_formula = NA) %>% 
          as_tibble() %>% 
          mutate(across(1:4, round, 2))) %>% 
  rename("Estimated peck rate" = Estimate,
         "Indicated expectation" = Bias_treatment) %>% 
    rbind(fitted(baseline_peck_model_zi, summary = T, re_formula = NA) %>% 
          as_tibble() %>%
          distinct(Estimate, .keep_all = T) %>% 
          mutate(across(1:4, round, 2)) %>% 
  rename("Estimated peck rate" = Estimate) %>% 
  mutate(`Indicated expectation` = "Baseline")) %>% 
  pander()
```

$~$

### Build Figure 2e-h

$~$

**Get posterior means and difference contrasts**

```{r}

# treatment model

peck_draws_treatment <-
  as_draws_df(peck_model_treatment) %>% 
  mutate(Hungry = exp(b_Bias_treatmentHungry),
         Satiated = exp(b_Bias_treatmentSatiated),
         diff_contrast = (Hungry - Satiated)) %>% 
  select(Hungry, Satiated, diff_contrast) %>%
  bind_cols(baseline_peck_predictions %>% select(Baseline_estimate)) %>% 
  pivot_longer(names_to = "Treatment", values_to = "Posterior_estimate", cols = 1:3) %>% 
  mutate(Predictor = "Allocated primer")


p6 <- 
    peck_draws_treatment %>% 
    filter(Treatment != "diff_contrast") %>% 
    ggplot(aes(x = Treatment, y = Posterior_estimate)) +
    stat_slab(aes(y = Baseline_estimate),
              linetype = 2, linewidth = 0.8, slab_fill = "white",
              colour = "black") +
    stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
                 point_interval = "median_qi", point_fill = "white",
                 shape = 21, point_size = 4, stroke = 1.5) +
    scale_fill_manual(values = met.brewer("Hiroshige", 2)) +
    coord_flip(ylim = c(0, 20)) +
    #geom_vline(xintercept = 0, linetype = 2) +
    #scale_y_continuous(breaks = c(, 0, 1)) +
    xlab("Allocated primer") +
    ylab("Estimated pecks per min") +
    theme_bw() + 
    theme(legend.position = "none",
          panel.grid.minor = element_blank(),
          text = element_text(size = 14))

p7 <-
  peck_draws_treatment %>% 
  filter(Treatment == "diff_contrast") %>% 
  ggplot(aes(y = Posterior_estimate)) + 
   stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
               point_interval = "median_qi", point_fill = "white",
               shape = 21, point_size = 4, stroke = 1.5, scale =0.5) +
  scale_fill_manual(values = met.brewer("Hiroshige")[4]) +
  coord_flip(ylim = c(-5, 12)) +
  geom_hline(yintercept = 0, linetype = 2, linewidth = 0.75) +
  #scale_y_continuous(breaks = c(, 0, 1)) +
  xlab(NULL) +
  ylab("Hungry - Satiated difference\ncontrast (pecks per min)") +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        text = element_text(size = 14))

# expectation model

peck_draws_expectation <-
  as_draws_df(peck_model_expectation) %>% 
  mutate(Hungry = exp(b_ExpectationHungry),
         Satiated = exp(b_ExpectationSatiated),
         diff_contrast = (Hungry - Satiated)) %>% 
  select(Hungry, Satiated, diff_contrast) %>% 
  bind_cols(baseline_peck_predictions %>% select(Baseline_estimate)) %>% 
  pivot_longer(names_to = "Treatment", values_to = "Posterior_estimate", cols = 1:3) %>% 
  mutate(Predictor = "Allocated primer")

p8 <-
  peck_draws_expectation %>% 
  filter(Treatment != "diff_contrast") %>% 
  ggplot(aes(x = Treatment, y = Posterior_estimate)) + 
  stat_slab(aes(y = Baseline_estimate),
              linetype = 2, linewidth = 0.8, slab_fill = "white",
              colour = "black") +
    stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
               point_interval = "median_qi", point_fill = "white",
               shape = 21, point_size = 4, stroke = 1.5) +
  scale_fill_manual(values = met.brewer("Hiroshige", 2)) +
  coord_flip(ylim = c(0, 20)) +
  #geom_vline(xintercept = 0, linetype = 2) +
  #scale_y_continuous(breaks = c(, 0, 1)) +
  xlab("Indicated expectation") +
  ylab("Estimated pecks per min") +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        text = element_text(size = 14))

p9 <-
  peck_draws_expectation %>% 
  filter(Treatment == "diff_contrast") %>% 
  ggplot(aes(y = Posterior_estimate)) + 
   stat_halfeye(aes(fill = Treatment), .width = c(0.66, 0.95), alpha = 0.9,
               point_interval = "median_qi", point_fill = "white",
               shape = 21, point_size = 4, stroke = 1.5, scale =0.5) +
  scale_fill_manual(values = met.brewer("Hiroshige")[4]) +
  coord_flip(ylim = c(-5, 12)) +
  geom_hline(yintercept = 0, linetype = 2, linewidth = 0.75) +
  #scale_y_continuous(breaks = c(, 0, 1)) +
  xlab(NULL) +
  ylab("Hungry - Satiated difference\ncontrast (pecks per min)") +
  theme_bw() + 
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        text = element_text(size = 14))
```

$~$

### Find the difference between baseline and observer estimates

**Table S5**. The degree to which each group of observer's overestimates feeding rate (number of ground pecks per minute)

```{r}
baseline_peck_predictions %>% select(Baseline_estimate) %>%  bind_cols(
  
  as_draws_df(peck_model_treatment) %>% 
    mutate(Hungry = exp(b_Bias_treatmentHungry),
           Satiated = exp(b_Bias_treatmentSatiated)) %>% 
    select(Hungry, Satiated)) %>% 
  mutate(`Bias treatment Satiated / Baseline` = Satiated / Baseline_estimate,
         `Bias treatment Hungry / Baseline` = Hungry / Baseline_estimate) %>% 
  select(contains("Bias")) %>% 
  pivot_longer(cols = everything(), values_to = "estimate", names_to = "Stat") %>% 
  group_by(Stat) %>% 
  summarise_draws("median", "sd", ~quantile(.x, probs = c(0.025, 0.975), na.rm = TRUE), .cores = 4) %>% 
  select(-variable) %>% 
  
  bind_rows(
    
    baseline_peck_predictions %>% select(Baseline_estimate) %>%  bind_cols(
      
      as_draws_df(peck_model_expectation) %>% 
        mutate(Hungry = exp(b_ExpectationHungry),
               Satiated = exp(b_ExpectationSatiated)) %>% 
        select(Hungry, Satiated)) %>% 
      mutate(`Expectation Satiated / Baseline` = Satiated / Baseline_estimate,
             `Expectation Hungry / Baseline` = Hungry / Baseline_estimate) %>% 
      select(contains("Expectation")) %>% 
      pivot_longer(cols = everything(), values_to = "estimate", names_to = "Stat") %>% 
      group_by(Stat) %>% 
      summarise_draws("median", "sd", ~quantile(.x, probs = c(0.025, 0.975), na.rm = TRUE), .cores = 4) %>% 
      select(-variable)
  ) %>% 
  pander()
```


# Figure 2

```{r, fig.height=12}
(p2 + p3) / (p4 + p5) / (p6 + p7) / (p8 + p9) +
   plot_annotation(tag_levels = 'a')
```

**Figure 2**. Posterior mean estimates and difference contrasts for observer estimated group foraging percentage and individual feeding rates. The coloured area is the posterior distribution and the white point is the mean estimate with associated 67% and 95% credible intervals.


# Session info

```{r}
sessionInfo() %>% pander
```

